---
title: 'HW #3: Monster Lab Meeting'
author: "Gaea Daniel"
date: "February 15, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
```{r}
#To load necessary packages
library(lattice)
library(latticeExtra)
library(Rcmdr)
library(RcmdrMisc)
library(RColorBrewer)
library(datasets)
#Import "White_wines.csv" data from Files
```

You are now the data slave to the principal investigator Dr. Vinca Monster. Dr. M is in the Grape Program at State U, and you are just a poor graduate student trying to get your degree. Dr. M is interested in wine preferences and the influences of physico-chemical properties on preferences. Her laboratory has gathered an extensive dataset on Portugese white varietals.


You will find the white_wines.csv file and its description in my github repo (https://github.com/vhertzb/Regression-1)[https://github.com/vhertzb/Regression-1].

Please use the techniques you have learned in the last two classes, specifically exploratory data analysis and linear regression, to determine association of the wine properties on preference. 

Prepare a report for presentation at the next Monster lab meeting about this dataset.

Rubric:

Exploration (summary statistics (the m's), univariate graphs, multivariate graphs)

```{r}
#To get the names of all the variables
variable.names(White_wines)
#To get the summary statistics for all the variables
summary(White_wines)
#To get univariate graphs for all the variables
histogram(~fixed.acidity, data=White_wines)
histogram(~volatile.acidity, data=White_wines)
histogram(~citric.acid, data=White_wines)
histogram(~residual.sugar, data=White_wines)
histogram(~chlorides, data=White_wines)
histogram(~free.sulfur.dioxide, data=White_wines)
histogram(~total.sulfur.dioxide, data=White_wines)
histogram(~density, data=White_wines)
histogram(~pH, data=White_wines)
histogram(~sulphates, data=White_wines)
histogram(~alcohol, data=White_wines)
histogram(~quality, data=White_wines)


#To get multivariate graphs
scatterplotMatrix(~fixed.acidity + volatile.acidity + citric.acid, data=White_wines)
scatterplotMatrix(~residual.sugar + chlorides + free.sulfur.dioxide + total.sulfur.dioxide, data=White_wines)
scatterplotMatrix(~density + pH + sulphates + alcohol, data=White_wines)
```

Regression (Models explored, diagnostics completed, final model choice, justification)

```{r}
#To get linear regression data
RegModel.1 <- 
  lm(quality~alcohol+chlorides+citric.acid+density+fixed.acidity+free.sulfur.dioxide+pH+residual.sugar+sulphates+total.sulfur.dioxide+volatile.acidity,
   data=whwi)
summary(RegModel.1)

#Linear regression data without variables where p<0.05 (chlorides, citric.acid, total.sulfur.dioxide) indicating a lack of significance
RegModel.1 <- 
  lm(quality~alcohol+density+fixed.acidity+free.sulfur.dioxide+pH+residual.sugar+sulphates+volatile.acidity,
    data=whwi)
summary(RegModel.1)
```

Please include a concluding paragraph (or two) about the implications of your findings.

If alcohol increases by 1 unit, then average quality rating will increase by 1.932e-01 units, with the other variables held constant.